---
title: "Assignment2"
output: html_document
date: "2023-03-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(formatR)
library(RSNNS)
library(neuralnet)
library(quantmod)
```
To do:
-Summary of plots
- Details of the strategy, representation, model figuration, implementation, parameters. 
- Calculation of profit using the weights
- Compare with the PSO 



**An overview of the of data you chose to work with (as usual, summary plots would be welcome). Working with one data set is fine but if you want to extend that to consider several assets then that is okay too.  (2 marks)**

Tractor Supply Co is a US based chain store that sells products for home improvement, agriculture, lawn and garden maintenence, livestock and pets.
```{r}
getSymbols("TSCO", src="yahoo", from="2020-01-01", to="2021-01-01")
str(TSCO) 
head(TSCO) 
```
```{r}
plot(TSCO)
```
```{r}
# Scaling the dataset features to avoid overfitting
scaledData = TSCO/sum(TSCO)
head(scaledData)
plot(scaledData)
```


```{r}
closeDF <- TSCO$TSCO.Close
head(closeDF)
```
**Details of your trading strategy and any specific decisions about the representation, fitness function, model configuration etc. along with details about implementation, any key parameters  etc... (9 marks)**

Creating a neural network to predict price based on opening price, closing price, volume, RSI, and EMA. 
```{r}
# Create lagged variables for the input features
lag_close = lag(TSCO$TSCO.Close, 1)
lag_high = lag(TSCO$TSCO.High, 1)
lag_low = lag(TSCO$TSCO.Low, 1)
lag_volume = lag(TSCO$TSCO.Volume, 1)
lag_rsi = lag(RSI(TSCO[,c("TSCO.Close")], n = 14), 1)
lag_ema = lag(EMA(TSCO[,c("TSCO.Close")], n = 9), 1)
```

```{r}
TSCOdf <- data.frame(date=index(lag_close), lag_close, lag_high, lag_low, lag_volume, lag_rsi, lag_ema)
# Calculatiing percentage of NAs
(colMeans(is.na(TSCOdf)))*100
```
```{r}
# Replacing the NA with 0
TSCOdf[is.na(TSCOdf)] <- 0
```

```{r}
train_data <- TSCOdf[1:203, 2:7]
train_data <- normalizeData(train_data)
colnames(train_data) <- colnames(TSCOdf)[2:7]

test_data <- TSCOdf[204:253, 2:7]
test_data <- normalizeData(test_data)
colnames(test_data) <- colnames(TSCOdf)[2:7]
```



```{r}
# Train the neural network
TSCO.nn <- neuralnet(TSCO.Close ~ TSCO.High + TSCO.Low + TSCO.Volume + rsi + EMA,
                     data = train_data,
                     hidden = c(10, 10, 10),
                     linear.output = TRUE,
                     threshold = 0.001,
                     stepmax = 1e5)
```

```{r, echo=FALSE, results=FALSE}
plot(TSCO.nn)
```


```{r}
TSCO.nn$net.result
```
```{r}
# Since COST.Close was normalised before training the network, it needs
# to be denormalised here. The resulting dataframe allows to compare
# the actual values with the predicted ones with a column showing the
# difference of actual - predicted.
predictions <- denormalizeData(compute(TSCO.nn, test_data)$net.result, getNormParameters(test_data))[, 1]

test_denormalized <- denormalizeData(test_data, getNormParameters(test_data))

actual_values <- denormalizeData(test_data[, 1], getNormParameters(test_data))[, 1]

difference <- actual_values - predictions

final_df <- data.frame(actual_values, predictions, difference)
print(final_df)
```


```{r}
plot(difference)
```
```{r}
predictionsDF <- data.frame(predictions)
test_denormalized <- data.frame(test_denormalized)
```

```{r}
sampleData <- data.frame(test_denormalized, predictions)
names(sampleData) <- c("COST.Close", "COST.High", "COST.Low", "COST.Volume", "rsi", "EMA", "predictions")
sampleData
```

Trading strategy - Calculate Moving Average for a 20 day period. Rules: Buy when current price is 

```{r}
train_data <- data.frame(train_data)
```

```{r}
window_size <- 20
moving_avg <- SMA(actual_values, n = window_size)
```

```{r}
trading_strategy <- function(price, ma, holding) {
  if (price > ma && holding == FALSE) {
    holding <- TRUE
    signal <- "buy"
  } else if (price < ma && holding == TRUE) {
    holding <- FALSE
    signal <- "sell"
  } else {
    signal <- "hold"
  }
  return(list(signal = signal, holding = holding))
}
```

```{r}
# Calculate profit
  holding <- FALSE
  cash <- 10000
  shares <- 0
  signals <- character(length = length(predictionsDF))
  for (i in 1:length(predictionsDF)) {
    # Get current price and moving average
    current_price <- test_data[i, "TSCO.Close"]
    current_ma <- moving_avg[length(moving_avg) - length(predictionsDF) + i]
    
    # Generate trading signal
    signal <- trading_strategy(current_price, current_ma, holding)
    signals[i] <- signal$signal
    
    # Execute trading signal
    if (signal$signal == "buy") {
      shares <- cash / current_price
      cash <- 0
      holding <- TRUE
    } else if (signal$signal == "sell") {
      cash <- shares * current_price
      shares <- 0
      holding <- FALSE
    }
  }
  final_value <- cash + shares * predictions[length(predictions)]
  profit <- final_value - 10000
```

```{r}
sampleData <- cbind(sampleData, signals)
sampleData
```

```{r} 
#Summarizing the performance by determining profit. 

rmse <- sqrt(mean((predictions - actual_values)^2))
rmse

```

